Equations & R Code

### 2016-07-06 manuscript/manuscript.Rmd
smal update to ms

Hints of the idea that diverse ecosystems are more stable through time than species-poor ecosystems go back as far as Darwin [@Darwin1859], who, in passing, mentions the `division of labor' that arises from niche differentiation among species [@Turnbull2013].

>>>>

Empirical tests of the prediction that species richness increases ecosystem stability have relied on both experimental and observational approaches.
Experimental tests involve manipulating the number of species present in a plot by randomly drawing a specific number of species from a pre-defined species pool [@Hector1999; @Tilman2001].
Results from such experimental tests, which have focused on plant species richness and the temporal stability of aboveground biomass production, have been surprisingly consistent: temporal stability is greater in communities with more species [@Tilman2006; @Hector2010].
Observational tests of the DSR require sampling across natural diversity gradients
